Towards a Machine Learning approach for Aggregate Computing

### 2021-08-17 paper-2021-woa-ac-ml.tex
more on multi'and many agent

\paragraph{Multi- and many-agent system}
%
An aggregate system is a multi-agent system
 and, often, a \emph{many}-agent system
 where a large number (hundreds or more)
 of autonomous entities are programmed to achieve 
 some collective behaviour by means of \emph{repeated} 
 sensing, computation, communication, and actuation steps.
%
\meta{TODO present approaches for learning in MAS, e.g., through prominent surveys}

>>>>

\paragraph{Multi- and many-agent system}
%
An aggregate system is a multi-agent system
 and, often, a \emph{many}-agent system
 where a large number (hundreds or more)
 of autonomous entities are programmed to achieve 
 some collective behaviour by means of \emph{repeated} 
 sensing, computation, communication, and actuation steps.
%
Due to the high stochasticity of the environment,
it is almost impossible to know and
program the optimal behaviour for all agents in advance.
This results in the need to create intelligent agents
so that they can learn the optimal behaviour and adapt to environmental changes.
%
In recent decades there has been an emerging trend in the use of reinforcement learning
 in multi-agent settings, as a powerful, robust and adaptive learning paradigm.
 Progress has been considerable and a wide range of algorithms are now available.

\meta{TODO present approaches for learning in MAS, e.g., through prominent surveys}
